%-------------------------
% Resume in Latex
% Author : Jasper Lagoyda
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{template}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
     {\Huge \scshape Jasper Gould Lagoyda} \\ \vspace{1pt}
    32 Rutland  APT 3R, Boston MA 02118 \\ \vspace{1pt}
    \small \href{tel:+xxxxxxxxxxxx}{ \raisebox{-0.1\height}\faPhone\ \underline{+202-534-9460} ~} \href{mailto:yourname@gmail.com}{\raisebox{-0.2\height}\faEnvelope\   \underline{jglagoyda@gmail.com}} ~ \\ 
    \href{linkedin.com/in/jasper-gould-lagoyda-93a255131}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{linkedin.com/in/jasper-gould-lagoyda-93a255131}}  ~
   % \href{https://github.com/Jglagoyda}{\raisebox{-0.2\height}\faGithub\ \underline{https://github.com/Jglagoyda}} ~
    \vspace{-8pt}
\end{center}
%-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Massachusetts Amherst}{Expected May 2024}
      { Bachelors of Science in Mathematics with a concentration in Applied Mathematics 
      } {Amherst, MA} 
  \resumeSubHeadingListEnd
  
 

%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
               \item Intro Computer Science(Java)
                \item C++ Programming
                \item Matlab Programing 
                \item Python 
                \item Multi-variable Calculus
                \item Linear Algebra 
                \item Differential Equations
                \item Chemistry 1 and 2 with Lab 
                \item College Physics Mechanics with Lab 
                \item Numerical Analysis
                \item Probability  
                \item Generative Models 
                \item Working knowledge of Linux/Command-line Unix
               % \item Meeting Note Taking 
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus Cleaners}{Jun 2022 -- August 2022} 
      {\underline{Store Clark}}{Boston, MA}
      \resumeItemListStart
        \resumeItem{\normalsize{ Provided customer service, addressing inquiries and ensuring high satisfaction levels. }}
        \resumeItem{\normalsize{Managed cash transactions accurately.}}
        \resumeItem{\normalsize{Organized and processed incoming orders efficiently, adhering to quality standards and timelines.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
 \resumeSubHeadingListStart
    \resumeSubheading
      {Bunker Hill Community College}{September 2020 -- May 2021} 
      {\underline{Executive Secretary for the Student Government Association (SGA)}} {Boston, MA}%{Boston MA} 
      \resumeItemListStart
        \resumeItem{\normalsize{Recorded minutes of SGA meetings.}}
        \resumeItem{\normalsize{Acted as parliamentarian for SGA meetings.}}
        \resumeItem{\normalsize{Managed SGA online accounts and documents.}}
        \resumeItem{\normalsize{Along with other members of the SGA, helped amend the SGA constitution. }}
        \resumeItem{\normalsize{Analyzed problems in the community and used creative thinking to solve the problems.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Access Partnership}{Jun 2017 -- Jul 2017} 
      {\underline{Summer Intern}}{Washington, DC}
      \resumeItemListStart
        \resumeItem{\normalsize{Assisted staff with  research on the Chilean government telecom regulator }}
        \resumeItem{\normalsize{Assisted staff with accounting in managing and organizing receipts.}}
        \resumeItem{\normalsize{Attended on a public policy panel on autonomous vehicles and took notes. }}
         \resumeItem{\normalsize{Aided in managing Twitter accounts.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}
%-----------PROGRAMMING SKILLS-----------

%-----------INVOLVEMENT---------------

\section{EXTRACURRICULAR}
 \resumeSubHeadingListStart
    \resumeSubheading{University of Massachusetts Amherst Chapter of SIAM}{ September 2023 - May 2024}{\underline{Founder and President}}{Amherst, MA}
           \resumeItemListStart
            \resumeItem{\normalsize{Founded and initiated Chapter.}}
            \resumeItem{\normalsize{ Achieved Chapter recognition from the Society for Industrial and Applied Mathematics, SIAM.}}
            \resumeItem{\normalsize{Recruited and led a team of Six people.}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading{University of Massachusetts Amherst Board Game Club}{ September 2023 - May 2024}{\underline{Events Coordinator}}{Amherst, MA}
           \resumeItemListStart
            \resumeItem{\normalsize{Organized a trip to Pax Unplugged in Philadelphia.}}
            \resumeItem{\normalsize{Worked with officers to plan and execute the trip.}}
            \resumeItem{\normalsize{Worked with University Student finance Team to provide payment for accommodations for trip  }}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading{NOLS Waddington Range Expedition}{Jun 2023 - Jul 2023}{\underline{Expectation Member}}{Mount Vernon, WA}
           \resumeItemListStart
            \resumeItem{\normalsize{Climbed Mountains, Geysers, and navigated woods and forest.}}
            \resumeItem{\normalsize{Worked with expedition members and Leaders to achieve objectives.  }}
            \resumeItem{\normalsize{Cooked food and helped make camp every night. }}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
 \vspace{-11pt}
\end{document}
